---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# cash-rate-scraper

This repository was created for demonstration purposes! 



It contains one script: `R/scrape_cash_rate.R`. This file downloads the [latest ASX cash rate implied yield curve PDF](https://www.asx.com.au/data/trt/ib_expectation_curve_graph.pdf), and attempts to parse the table from the PDF. The table is saved as a CSV in `daily_data`. The file `combined_data/all_data.Rds` contains a dataframe that is the combination of all the daily data CSVs. 

Note that this script is brittle and was hacked together quickly. It will probably break! I offer no assurance that this will continue to work, or that the data extracted using this script will be free of errors.

The `.github/workflows/refresh_data.yaml` file contains the instructions to GitHub Actions to tell it to run `scrape_cash_rate.R` each day and commit the results in this repo.

Please fork/copy/modify as you see fit.

# Graph!

```{r, echo = FALSE}
source(file.path("R", "viz_cash_rate.R"))

viz_1

viz_2 

viz_3
```
