---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# cash-rate-scraper

The key script in this repo is `R/scrape_cash_rate.R`. This file parses market expectations for the cash rate based on the [latest ASX cash rate implied yield curve](https://www.asx.com.au/markets/trade-our-derivatives-market/futures-market/rba-rate-tracker). 

The data is saved as a CSV in `daily_data`. The file `combined_data/all_data.Rds` contains a dataframe that is the combination of all the daily data CSVs. 

Note that there was a gap in the data collection between 1 July and 20 July, as the ASX changed its website.

I offer no assurance that this will continue to work, or that the data extracted using this script will be free of errors.

The `.github/workflows/refresh_data.yaml` file contains the instructions to GitHub Actions to tell it to run `scrape_cash_rate.R` each day and commit the results in this repo.

Please fork/copy/modify as you see fit.

# Graphs!

The file `R/viz_cash_rate.R` produces visualisations of this data, which are shown below.

```{r, echo = FALSE}
source(file.path("R", "viz_cash_rate.R"))

viz_1

viz_2 

viz_3

viz_4
```
